\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-09 Thesis.tex
pre changes version

Normally we only have one path for a narration. That is true for books, movies, Facebook timelines, and also slide-based presentations. For three out of those four this has not changed in decades. With the advancement of technology, we are, however, able to change the way presentations and their narratives work. In essence we should be able to make it possible to link content that logically belongs together, in other words, content that is semantically close. Through that it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined path, but rather along the path that will allow the audience to make the most out of the presentation.\\

@@

Building on the preliminaries, we will now commence the journey towards building a more effective presentation format. To create these presentations automatically, the tool RPresentation \cite{npentrel:npentrel15} was created.\\

With the OMDoc framework and its tools it is possible to write down course notes or other documents in \stex. From this document we can then, in theory, seamlessly create slides both in PDF format as well as in XHTML format. Using a test document that is supposed to explain the pythagorean theorem and related topics, the \sys tool can retrieve the the order of the slides as well as dependencies. This combined creates an information graph which we us to create a relational presentation out of the annotated document.\\

\ednote{should this be longer?}

@@

In our system \sys, we parse the \stex files to retrieve the traditional narrative the writer intended to use. This is the first narrative layer, which we will refer to as a \textit{primary narrative path} since we go from slide to slide on our path to the end of the presentation. To create this primary narrative path we need to add several slides with increasing x-coordinates as shown in \autoref{fig:narrativePathCode}. This code creates \ednote{insert image of just the primary narrative path from example}. \\

@@

@@

The primary narrative path is the traditional path a presenter normally uses when preparing a PowerPoint presentation. This path happens to also contain temporal information. This temporal information is what we extracted from the \stex as the order in which the slides (or the information on the slides) should appear in.\\

This temporal information is also used to create narrative paths for subsections of the whole presentation that only explain one topic. In that these narrative paths are similar to the guided tours mentioned in \autoref{sec:relatedworks} in that they aim to explain one topic but they are different in that they just reuse slides that have already occurred. \ednote{use Annie example} In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own. These occur on different levels as explained in the next section \autoref{sec:levels}.\\

@@

\ednote{show inclusion graph and add an example to explain further}

@@

@@

@@

\subsection{Technical Details}
\label{sec:wp4}

@@

\ednote{lmh not working :(}

@@

>>>>

Normally we only have one path for a narration. That is true for books, movies, Facebook timelines, and also traditional slide-based presentations. For three out of those four this has not changed in decades. With the advancement of technology, we are however able to change the way presentations and their narratives work. We can make it possible to link content that logically belongs together, in other words, content that is semantically close. Through the linking of content it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined path, but rather along the path that will allow the audience to make the most out of the presentation.\\

@@

Building on the preliminaries, we will now commence the journey towards building a more effective presentation format. To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created. The implementation details of \sys will be discussed in \ref{sec:implementation}\\

With the OMDoc framework and its tools it is possible to write down course notes or other documents in \stex. From this document we can then, in theory, seamlessly create slides both in PDF format as well as in XHTML format. Using a test document that is supposed to explain the pythagorean theorem and related topics, the \sys tool can retrieve the the order of the slides as well as dependencies. The order of the slides and their dependencies combined lead to an information graph which we then use to create a relational presentation out of the annotated document.\\

@@

In our system \sys, we parse the \stex files to retrieve the traditional narrative the writer intended to use. This is the first narrative layer, which we will refer to as a \textit{primary narrative path} since we go from slide to slide on our path to the end of the presentation. To create this primary narrative path we need to add several slides with increasing x-coordinates as shown in \autoref{fig:narrativePathCode}. This code snippet creates the narrative path portrayed in \autoref{fig:primaryNarrativePath}.\\

@@

\begin{wrapfigure}{c}{\textwidth}
\vspace{-20pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.97\textwidth]{assets/final/primaryNarrativePath2}
    }
  \end{center}
\vspace{-16pt}
  \caption{Primary Narrative Path}
  \label{fig:primaryNarrativePath}
\vspace{12pt}
\end{wrapfigure}

@@

The primary narrative path is the traditional path a presenter normally uses when preparing a PowerPoint presentation. This path happens to also contain temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}. This temporal information is what we extracted from the \stex as the order in which the slides (or the information on the slides) should appear in.\\

This temporal information is also used to create narrative paths for subsections of the whole presentation that only explain one topic. In that these narrative paths are similar to the guided tours mentioned in \autoref{sec:relatedworks} in that they aim to explain one topic but they are different in that they just reuse slides that have already occurred. Going back to our example of Annie, an example of a subsection would be the information concerning angles. In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own. These occur on different levels as explained in the next section \autoref{sec:levels}.\\

@@

\begin{wrapfigure}{c}{\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/inclusionGraphPythagorean}
    } 
\vspace{-5pt}
  \caption{Inclusion Graph for the Pythagorean Theorem}
  \label{fig:inclusionGraph}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

\begin{wrapfigure}{c}{\textwidth}
\vspace{-50pt}
\end{wrapfigure}

The graph for CS looks more like this:

\begin{wrapfigure}{c}{\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.3\textwidth]{assets/final/inclusionGraphCS}
    } 
\vspace{-5pt}
  \caption{Inclusion Graph for Gen CS}
  \label{fig:inclusionGraph}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

\begin{wrapfigure}{c}{\textwidth}
\vspace{-50pt}
\end{wrapfigure}
sda

@@

\begin{wrapfigure}{c}{\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/depGraphPythagorean}
    } 
\vspace{-5pt}
  \caption{Dependency Graph}
  \label{fig:depGraphPythagorean}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

\begin{wrapfigure}{c}{\textwidth}
\vspace{-50pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{c}{0.97\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/fullPresentation}
    } 
\vspace{-5pt}
  \caption{Presentation Overview}
  \label{fig:fullPresentation}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

\begin{wrapfigure}{c}{\textwidth}
\vspace{-50pt}
\end{wrapfigure}

@@

\ednote{show possible paths thru presentation}

\subsection{Technical Details}
\label{sec:implementation}

\ednote{this is relatively shallow, about the implementation we only get to know that it is in Java. An architecture diagram would be helpful, and if you have that, you can explain it. That will give you something to guide the level of presentation.}

\ednote{where to put the screenshot hack?}

@@

@@

\ednote{think of more extensions when you write up the rest}
